Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-28 draft/ms_v5.tex
PSF magnitude

    We now investigate the performance of the PSF photometry in each of the five bands
    independently. 
    Fig \ref{fig:psf_mag} shows the difference between the input magnitude versus the
    \hscpipe{} \forced{} PSF magnitude ($\Delta \mathrm{mag}_{\mathrm{PSF}}$) as a 
    function of input magnitude. 
    We separate these stars into seven input magnitude bins.  
    In each bin, we characterize the \textbf{precision} of the PSF magnitude using 
    the standard deviation of the $\Delta \mathrm{mag}_{\mathrm{PSF}}$ distribution.
    Meanwhile, we characterize the \textbf{accuracy} of the PSF magnitude via the 
    mean magnitude difference in each bin. 
    This also informs us whether the PSF photometry is biased at certain input 
    magnitude.

    The overall performance of the \hscpipe{} \forced{} PSF magnitude is excellent. 
    The median $i$-band magnitude difference for the \tract{} with 0.45\asec{} seeing 
    is ${\sim}0.015$ mag (${\sim}1.5$\%) at $i_{\mathrm{Input}}{\sim}19.0$ mag. 
    At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of the PSF magnitude is 
    ${\sim}3$\% level (${\sim}0.036$ mag average difference).
    At $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy decreases to
    ${\sim}7$\% with an average ${\sim}0.072$ mag difference.

    The accuracy of the PSF photometry for the bad-seeing \tract{} shows a similar 
    performance at $i_{\mathrm{Input}}<23.5$ mag. 
    At fainter magnitudes, the accuracy slightly degrades. 
    The bad-seeing \tract{} displays a performance of ${\sim}5$\% accuracy at
    $i_{\mathrm{Input}}{\sim}24.0$ mag and ${\sim}11$\% accuracy at
    $i_{\mathrm{Input}}{\sim}25.2$ mag.
    \citet{HSCDR1} evaluates the accuracy of PSF photometry via external comparisons
    with the PS1, PV2, and SDSS data at $i<21$ mag, and finds a 1-2\% level accuracy,
    which is consistent with our results. 
    However, at fainter magnitudes, external comparisons become difficult due to the 
    lack of imaging matched to HSC depths.
    The results from \synpipe{} hence provide useful evaluations of the accuracy of 
    the HSC photometry down to our detection limit\footnote{Strictly speaking, the 
    uncertainties reported here should be considered as the lower limit because 
    \synpipe{} currently does not consider PSF modeling uncertainties}.

    Figure \ref{fig:psf_mag} also shows that the accuracy of the PSF photometry is 
    not filter dependent. 
    The accuracy of forced PSF magnitudes in $r$ and $z$ is similar to the $i$-band. 
    For $r$ band we find 1.5-4.0\% at $r_{\mathrm{Input}} < 24.0$ mag and ${\sim}8$\% 
    at $r_{\mathrm{Input}}{\sim}25.2$. 
    For $z$-band we find 1.0-5.0\% at $z_{\mathrm{Input}} < 24.0$ mag and ${\sim}10$\% 
    down to $z_{\mathrm{Input}}{\sim}25.2$ mag).

    The accuracy in the $g$ and $y$ bands becomes slightly worse at the very faint end. 
    For $g$ band, the accuracy is 1.5-7.0\% at $g_{\mathrm{Input}} < 24.0$ mag and is
    ${\sim}13$\% down to $25.2$ mag.
    For $y$ band, we find 1.5-5.0\% accuracy at $y_{\mathrm{Input}} < 23.0$ mag and
    ${\sim}12$\% down to $24.0$ mag. 
    These differences are however consistent with the differences in the seeing 
    conditions between the filters

    The PSF photometry for relatively isolated stars is unbiased in the $i$ and $z$ 
    bands down to faint magnitudes. 
    For the $g$, $r$, and $y$ bands, we find small offsets between the input and 
    recovered magnitude. 
    \hscpipe{} tends to underestimate the fluxes of stars in these bands by 
    ${\sim}0.01-0.02$ mag. 
    The exact cause of this offset is unclear but the levels of bias is quite small 
    and not a major concern.

@@

%% ------------------------------------------------------------------------------------ %%
\subsubsection{Accuracy of PSF colors}

>>>>

    We now investigate the performance of the PSF photometry in each of the five bands
    independently. 
    Fig \ref{fig:psf_mag} shows the difference between the input magnitude versus the
    \hscpipe{} \forced{} PSF magnitude ($\Delta \mathrm{mag}_{\mathrm{PSF}}$) as a 
    function of input magnitude. 
    We separate these stars into seven input magnitude bins.  
    In each bin, we characterize the statistical \textbf{precision} of the PSF 
    magnitude using the standard deviation of the $\Delta \mathrm{mag}_{\mathrm{PSF}}$ 
    distribution.
    Meanwhile, we characterize the statistical \textbf{accuracy} of the PSF magnitude 
    via the mean magnitude difference in each bin. 
    This also informs us whether the PSF photometry is biased at certain input 
    magnitude.

    The overall performance of the \hscpipe{} \forced{} PSF magnitude is excellent. 
    The median $i$-band PSf magnitude precision for the \texttt{goodSeeing} \tract{} 
    is ${\sim}0.015$ mag (${\sim}1.5$\%) at $i_{\mathrm{Input}}{\sim}19.0$ mag. 
    At $i_{\mathrm{Input}}{\sim}24.0$ mag, the precision of the PSF magnitude is 
    at ${\sim}3$\% level (${\sim}0.036$ mag average difference).
    At $i_{\mathrm{Input}}{\sim}25.2$ mag, the precision decreases to
    ${\sim}7$\% with an average ${\sim}0.072$ mag difference.

    The precision of PSF magnitude for the \texttt{badSeeing} \tract{} shows similar 
    performance at $i_{\mathrm{Input}}<23.5$ mag. 
    At fainter magnitudes, the precision slightly degrades. 
    The \texttt{badSeeing} \tract{} has ${\sim}5$\% precision at
    $i_{\mathrm{Input}}{\sim}24.0$ mag and ${\sim}11$\% precision at
    $i_{\mathrm{Input}}{\sim}25.2$ mag.
    \citet{HSCDR1} evaluates the precision of PSF magnitude via external comparisons
    with the PS1, PV2, and SDSS data at $i<21$ mag, and finds it at 1-2\% level,
    which is consistent with our results. 
    However, at fainter magnitudes, external comparisons become difficult due to the 
    lack of imaging matched to HSC depths.
    The results from \synpipe{} hence provide useful evaluations of the precision of 
    the HSC photometry down to our detection limit, though, strictly speaking, the 
    precision reported here should be considered as upper limits because 
    \synpipe{} currently does not consider the systematic uncertainties in PSF 
    modeling.

    Figure \ref{fig:psf_mag} also shows that the precision of the PSF photometry is 
    not filter dependent. 
    The precision of \forced{} PSF magnitudes in $r$ and $z$ is similar to the results
    for $i$-band. 
    For $r$ band we find 1.5-4.0\% precision at $r_{\mathrm{Input}} < 24.0$ mag and 
    ${\sim}8$\% precision at $r_{\mathrm{Input}}{\sim}25.2$. 
    For $z$-band we find 1.0-5.0\% precision at $z_{\mathrm{Input}} < 24.0$ mag and 
    ${\sim}10$\% precision down to $z_{\mathrm{Input}}{\sim}25.2$ mag).

    The precision for $g$ and $y$ bands becomes slightly worse at the very faint end. 
    For $g$ band, the precision is 1.5-7.0\% at $g_{\mathrm{Input}} < 24.0$ mag and is
    ${\sim}13$\% down to $25.2$ mag.
    For $y$ band, we find 1.5-5.0\% precision at $y_{\mathrm{Input}} < 23.0$ mag and
    ${\sim}12$\% down to $24.0$ mag. 
    These differences are however consistent with the differences in the seeing 
    conditions between the filters

    The PSF photometry for relatively isolated stars is accurate and unbiased in $i$ 
    and $z$ bands down to faint magnitudes. 
    For the $g$, $r$, and $y$ bands, we find mean $\Delta \mathrm{mag}_{\mathrm{PSF}}$
    that are close to the PSF flux errors estimated by \hscpipe{}.  
    \hscpipe{} tends to underestimate the fluxes of stars in these bands by 
    ${\sim}0.01-0.02$ mag. 
    The exact cause of this offset is unclear but the levels of bias is quite small 
    and not a major concern.

@@

%% ------------------------------------------------------------------------------------ %%
\subsubsection{Precision and Accuracy of PSF colors}
